A pipeline to analyse time-course gene expression data

### 2019-08-09 scripts/manuscript.Rmd
update plot_centroids for legend, etc

```{r fig.height=6, fig.width=6}
top_DE_genes_pval = names(sort(pvalue)[1:12])
plot_genes(data[top_DE_genes_pval, ], splines_model,
		   colors=ann_colors$Group, smooth=TRUE)
```

@@

```{r fig.height=6, fig.width=6}
plot_centroids(kmeans_clusters$centroids, splines_model,
		       colors=ann_colors$Group,
		       smooth=TRUE)
```

>>>>

```{r fig.height=6, fig.width=6}
top_DE_genes_pval = names(sort(pvalue)[1:12])
plot_genes(data[top_DE_genes_pval, ], splines_model,
    colors=ann_colors$Group, smooth=TRUE,
    mar=c(1.5,2.5,2,0.1),legendArgs=list(title="Treatment"),
    mfrow=c(3,5))
```

@@

```{r fig.height=6, fig.width=6}
plot_centroids(kmeans_clusters$centroids, splines_model,
    colors=ann_colors$Group,
    smooth=TRUE,legend=TRUE,
    legendArgs=list(title="Treatment",cex=2))
```
